### 2018-12-10 paper/paper.tex
Spelling grammar corrections

            This paper has shown that the usage of machine learning alone on email body text 
            along with a few other features can preform the classification well. 
            However, our metrics are lower
            than the other papers we are comparing against ourselves. Adding more features
            that aren't word based may help even more with performance and also increasing the
            size of the dataset would help as well. We also recognize the limitations of
            this implementation lending itself to only classify emails from the early 2000s, as
            we did no testing on modern email data which may have a distribution that doesn't
            work well with our implementation.
        \nocite{*}
        \bibliography{paper} 
        \bibliographystyle{alpha}
    \end{multicols}
\end{document}

>>>>

            This paper has shown that the usage of machine learning alone on email body text 
            along with a few other features can perform the spam classification task well. 
            However, our metrics are lower
            than the other papers we are comparing against ourselves. Adding more features
            that aren't word based may help even more with performance and also increasing the
            size of the dataset would help as well. We also recognize the limitations of
            this implementation lending itself to only classify emails from the early 2000s, as
            we did no testing on modern email data which may have a distribution that doesn't
            work well with our implementation.
        \nocite{*}
        \bibliography{paper} 
        \bibliographystyle{alpha}
    \end{multicols}
\end{document}
